---
title: "data_visualizations"
author: "ASM"
date: "09/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(dplyr)
library(lme4)
library(lmerTest)
library(afex)
library(gazer)
library(ggiraph)
library(ggiraphExtra)
library(ggeffects)
library(sjPlot)
library(ggExtra)
```

##------------------- Load the cleaned data & prepare for analyses-------------------------------------##

```{r}
load(here("merged_data_sets/arch_final.Rda"))

arch_re_zero<- arch_final%>%
  group_by(studio_project_name, studio_test_name, trial_number, recording_name)%>%
  mutate(trial_from_zero = recording_timestamp-min(recording_timestamp))%>%
  group_by(studio_project_name)%>%
  mutate(noun_onset = case_when(studio_project_name=="CompMix-36"~trial_from_zero-3000,
                                studio_project_name=="LearnMix-36"~trial_from_zero-4500,
                                studio_project_name=="Mix-20"~trial_from_zero-5400,
                                studio_project_name=="Mix-14"~trial_from_zero-5400,
                                studio_project_name=="CogMisp-24"~trial_from_zero-1500))%>%
  ungroup()%>%
  rename(target_side=target, distractor_side=distractor,
         gaze_point_x= gaze_point_x_adc_spx, 
         gaze_point_y = gaze_point_y_adc_spx)%>%
  filter(gaze_point_x>=0 & gaze_point_x<= 1920)%>% #keeps only observations that are in the screen
  filter(gaze_point_y>=0 & gaze_point_y<=1200)%>%
  filter(!is.na(gaze_point_x))%>% #gets rid of the observations where tobii didn't get any reading
  filter(!is.na(gaze_point_y))%>%
  filter(!is.na(validity_left)) %>%
  filter(!is.na(validity_right)) %>%
  filter(validity_left<= 1)%>%
  filter(validity_right <= 1)%>%
  mutate(target = case_when(gaze_point_x >= target_x_min&gaze_point_x <= target_x_max&gaze_point_y >= target_y_min&gaze_point_y <= target_y_max~TRUE, 
                            TRUE~FALSE))

```


##-------------------Create trial language column to describe the language in which the babies were tested on-------------------------------------##
```{r}
arch_re_zero <- arch_re_zero%>%
  ungroup()%>%
  group_by(studio_test_name, eng_exp, fre_exp)%>%
  mutate(trial_lang = case_when(str_detect(studio_test_name,"E")~ "english",
                                str_detect(studio_test_name, "F")~ "french"))
```


##-------------------center age and experience-------------------------------------##
```{r}
#centering to an easy to interpret value that is close to the mean, 25 months for age and 50% for experience.
arch_re_zero<- arch_re_zero%>%
  mutate(exp_to_target_lang = case_when(trial_lang == "english" ~ eng_exp,
                                        trial_lang == "french" ~ fre_exp)) %>%
  mutate(exp_target_lang_prop = exp_to_target_lang/100)

#mean(arch_re_zero$age_months)#25.79
#mean(arch_re_zero$exp_target_lang_prop) #0.57

 arch_re_zero_c<- arch_re_zero %>%
  mutate(age_centered = age_months-25) %>%
   mutate(exp_centered =exp_target_lang_prop - .50)
```


##------Preparing for Additive model predicted values visualization----##
```{r}
for_lmm_viz <- arch_re_zero_c

for_lmm_viz <- for_lmm_viz %>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  group_by(recording_name, subject_id, trial_number, media_name, age_months,exp_target_lang_prop)%>%
  summarise(samples_total=sum(target==TRUE, target==FALSE ),
            samples_target=sum(target))%>%
  mutate(prop_looking= samples_target/samples_total)
lmm_viz_aditive <- lmer (prop_looking ~ exp_target_lang_prop + age_months + (1|subject_id) + (1|media_name), data = for_lmm_viz)
```

##---Additive model predicted values visualization----##
```{r}
#using plot_model from sjplot in brackets added the values in which to predict effects so that the function does not extrapolate.
x<- plot_model(lmm_viz_aditive, type="eff", terms = c("age_months[14,20, 26, 32, 38, 44, 48] ", "exp_target_lang_prop[1 , 0.70, 0.39]"), line.size = 0.8, colors = c("#feb24c", "#d7301f", "#7f0000"),
           legend.title = "Exposure bins (percentage range)", title = "Predicted values of looking accuracy for the additive model")

#changing the legend levels to ra-name the groups in a more appropriate way
x$data$group_col<- as.character(x$data$group_col)
x$data$group_col<- factor(x$data$group_col)
levels(x$data$group_col)<- c("10-39", "40-70", "71-100")

x + theme_bw() +
  xlab("Age (months)")+
  ylab("Proportion looking to target")+
  ylim(0.4, 1.0)+
  xlim(14, 48)+
  geom_hline(yintercept = 0.5 , linetype = "dashed")+
  annotate("text", y=0.53, x=30, label="Chance looking to target", size=8)+
  guides (col= guide_legend(reverse= TRUE))+
  theme(legend.text = element_text(size = 22), legend.title = element_text(size = 22), plot.title = element_text(size = 30), axis.title = element_text(size = 30), axis.text = element_text(size = 30))   


ggsave("predicted_values.png", dpi = "print", width = 16, height = 8, units = "in")
```

##----Time course plots----##
```{r}
tc <- arch_re_zero%>%
  mutate(exp_bins = case_when(exp_target_lang_prop >= 0.1 & exp_target_lang_prop <=.39 ~"10-39",
                              exp_target_lang_prop >= .40 & exp_target_lang_prop <=.70 ~"40-70",
                              exp_target_lang_prop >=.71 & exp_target_lang_prop <=1 ~"71-100")) %>%
  mutate(age_bins= case_when(age_months >=14 & age_months<=20.9~"14-20 (m)",
                             age_months >=21 & age_months<=30.9~"21-30 (m)",
                             age_months>=31 & age_months<=48.9~"31-48 (m)"))
tc_graph <- tc%>%
  filter(noun_onset>=360 & noun_onset<=3000)%>%
  group_by(age_bins,exp_bins, interval = ifelse(ceiling(noun_onset/100) == 0, 100, ceiling(noun_onset/100)*100))%>%
  summarise(looking=mean(target, na.rm=T))

tc_graph %>%
  ggplot(aes(x=interval, y=looking, color=exp_bins))+
  geom_line(size=1)+
  #    stat_summary(aes(y = looking), fun.y=mean, colour="black", geom="line", size=0.8, alpha=0.5)+
  facet_grid(~age_bins)+
  scale_y_continuous(limits = c(0,1))+
  labs(x="Time from noun onset (ms)", 
       y= "Proportion looking to target")+
  ggtitle("Time series of infant looking by age group divided by experience")+
  scale_color_manual(name= "Exposure bins (percentage range)", values = c("#feb24c", "#d7301f", "#7f0000"))+
  theme_bw()+
  theme(legend.text = element_text(size = 22), legend.title = element_text(size = 22), 
        plot.title = element_text(size = 30), axis.title = element_text(size = 30), 
        axis.text = element_text(size = 22), strip.text.x = element_text(size = 22)) +
  guides (col= guide_legend(reverse= TRUE))

ggsave("time_course.png", dpi = "print", width = 16, height = 8, units = "in")

reversed <- tc%>%
  filter(noun_onset>=360 & noun_onset<=3000)%>%
  group_by(age_bins,exp_bins, interval = ifelse(ceiling(noun_onset/100) == 0, 100, ceiling(noun_onset/100)*100))%>%
  summarise(looking=mean(target, na.rm=T))%>%
  ggplot(aes(x=interval, y=looking, color=age_bins))+
  geom_line(size=1)+
  #    stat_summary(aes(y = looking), fun.y=mean, colour="black", geom="line", size=0.8, alpha=0.5)+
  facet_grid(~exp_bins)+
  scale_y_continuous(limits = c(0,1))+
  labs(x="time from noun onset (ms)", 
       y= "proportion looking to target")+
  ggtitle("time series of infant looking by age group divided by experience")+
  scale_color_manual(values = c("#feb24c", "#ef6548", "#d7301f", "#7f0000"))+
  theme(legend.text = element_text(size = 15), legend.title = element_text(size = 15), plot.title = element_text(size = 20), axis.title = element_text(size = 18), axis.text = element_text(size = 15)) 
  theme_bw()+
  guides (col= guide_legend(reverse= TRUE))

```

##-----Marginal histogram plot for age and experience participant distributions----##
```{r}

m<- arch_re_zero #but without age centered

pm<- m %>%
  ggplot(aes(x=age_months, y=exp_to_target_lang)) +
  geom_point() +
  theme(legend.position="none")+
  xlab("Age(months)") +
  ylab("Experience with target language (%)")+
  theme_bw()

marginal<- ggMarginal(pm, type="histogram", aes(y=after_stat(count)),
           xparams = list(binwidth = 12, fill= "#fc8d59"),
           yparams = list(binwidth = 30, fill= "#91cf60"))
print(marginal)
ggsave("marginal_plot.jpg")

```

##---- Counting amount of children per cell in the by experience by age bins ----------##
```{r}

count_exp<- tc %>%
  distinct(recording_name, exp_bins) %>%
  group_by(exp_bins) %>%
  tally()

count_exp_age<- tc %>%
  distinct(recording_name, exp_bins, age_bins) %>%
  group_by(exp_bins, age_bins) %>%
  tally()

```

##----- Additive model predicted AND raw values visualization----##
```{r}
#Plotting raw data with predicted data

y<- plot_model(lmm_viz_aditive, type="eff", terms = c("age_months[14,20, 26, 32, 38, 44, 48] ", "exp_target_lang_prop[1 , 0.65, 0.39]"), line.size = 0.8, colors = c("#feb24c", "#d7301f", "#7f0000"),
           legend.title = "Exposure bins (percentage range)", title = "Predicted values of looking accuracy for the additive model", show.data =  T)


y + theme_bw() +
  xlab("Age (months)")+
  ylab("Proportion looking to target")+
  ylim(0.4, 1.0)+
  xlim(14, 48)+
  geom_hline(yintercept = 0.5 , linetype = "dashed")+
  annotate("text", y=0.53, x=30, label="Chance looking to target", size=8)+
  guides (col= guide_legend(reverse= TRUE))+
  theme(legend.text = element_text(size = 22), legend.title = element_text(size = 22), plot.title = element_text(size = 30), axis.title = element_text(size = 30), axis.text = element_text(size = 30))   


ggsave("real_and_predicted_values.png", dpi = "print", width = 16, height = 8, units = "in")


```


```{r}
x<- plot_model(lmm_viz_aditive, type="eff", terms = c("age_months[14,20, 26, 32, 38, 44, 48] ", "exp_target_lang_prop[1 , 0.70, 0.39]"), line.size = 0.8, colors = c("#feb24c", "#d7301f", "#7f0000"),
           legend.title = "Exposure to target language (proportion)", title = "Predicted values of looking accuracy for the additive model", show.data = T)


x + theme_bw() +
  xlab("Age (months)")+
  ylab("Proportion looking to target")+
  ylim(0.4, 1.0)+
  xlim(14, 48)+
  geom_hline(yintercept = 0.5 , linetype = "dashed")+
  annotate("text", y=0.53, x=30, label="Chance looking to target", size=8)+
  guides (col= guide_legend(reverse= TRUE))+
  theme(legend.text = element_text(size = 22), legend.title = element_text(size = 22), plot.title = element_text(size = 30), axis.title = element_text(size = 30), axis.text = element_text(size = 30))   

```


```{r}
## Demonstration that average and prop is the same in the time course graphs.

tc2 <- arch_re_zero%>%
  mutate(exp_bins = case_when(exp_target_lang_prop >= 0.1 & exp_target_lang_prop <=.25 ~".25",
                              exp_target_lang_prop >= .26 & exp_target_lang_prop <=.5 ~".5",
                              exp_target_lang_prop >=.51 & exp_target_lang_prop <=.75 ~".75",
                              exp_target_lang_prop >=.76 & exp_target_lang_prop <=1 ~"1"))%>%
  mutate(age_bins= case_when(age_months >=14 & age_months<=20.9~"14-20 (m)",
                             age_months >=21 & age_months<=28.9~"21-28 (m)",
                             age_months >=29 & age_months<=36.9~"29-36 (m)",
                             age_months>=37 & age_months<=48.9~"37-48 (m)"))
tc2%>%
  filter(noun_onset>=360 & noun_onset<=3000)%>%
  group_by(age_bins,exp_bins, interval = ifelse(ceiling(noun_onset/100) == 0, 100, ceiling(noun_onset/100)*100))%>%
  summarise(samples_total=sum(target==TRUE, target==FALSE ),
            samples_target=sum(target))%>%
  mutate(prop_looking= samples_target/samples_total)%>%
  ggplot(aes(x=interval, y=prop_looking, color=exp_bins))+
  geom_line(size=1)+
  #    stat_summary(aes(y = looking), fun.y=mean, colour="black", geom="line", size=0.8, alpha=0.5)+
  facet_grid(~age_bins)+
  scale_y_continuous(limits = c(0,1))+
  labs(x="Time from noun onset (ms)", 
       y= "Proportion looking to target")+
  ggtitle("Time series of infant looking by age group divided by experience")+
  scale_color_manual(name= "Exposure bins (proportion)", values = c("#feb24c", "#ef6548", "#d7301f", "#7f0000"))+
  theme_bw()+
  theme(legend.text = element_text(size = 22), legend.title = element_text(size = 22), 
        plot.title = element_text(size = 30), axis.title = element_text(size = 30), 
        axis.text = element_text(size = 22), strip.text.x = element_text(size = 22)) +
  guides (col= guide_legend(reverse= TRUE))

```


```{r}
